Evaluation of Types

### 2020-05-16 evaluation/R/evaluate-type-analysis.Rmd
Fix vector na

old_theme <- theme_set(theme_bw() + theme(text = element_text(size = 15), panel.border = element_blank()))

@@

```{r vector-na-type, eval=TRUE, echo=FALSE}
vector_na_data <-
type_analysis_data %>%
filter(kind == "vector-na") %>%
group_by(type) %>%
summarize(count = n()) %>%
ungroup() %>%
arrange(desc(count)) %>%
mutate(percentage = round(100 * count / sum(count), 2),
       cumulative_percentage = round(100 * cumsum(count) / sum(count), 2))

>>>>

old_theme <- theme_set(theme_bw() + theme(text = element_text(size = 20), panel.border = element_blank()))

@@

```{r vector-na-type, eval=TRUE, echo=FALSE}
vector_na_data <-
type_analysis_data %>%
filter(kind == "^vector") %>%
group_by(type) %>%
summarize(count = n()) %>%
ungroup() %>%
arrange(desc(count)) %>%
mutate(percentage = round(100 * count / sum(count), 2),
       cumulative_percentage = round(100 * cumsum(count) / sum(count), 2))
